\protect Connecting every bit of knowledge: \\ The structure of Wikipedia's First Link Network

### 2016-04-27 writeup/2016-04wikipedia-network/wikipedia-network-revtex4-combined.tex
draft complete

\documentclass[pre,twocolumn,twoside,byrevtex,superscriptaddress,floatfix]{revtex4-1}

@@

One possible path through the FLN is a {\it cycle} or a group of articles 
linking to one another inside a loop. In our sample network 
(Fig.~\ref{fig:Traversal Visits}) 
a 3-cycle exists among nodes A, B, and C. 
We can readily identify
the types of cycle structures within the FLN
and rank each by 
the number of references directed towards a cycle.

We can also form and rank {\it basins} in the network by identifying groups of 
path-connected articles, not necessarily forming a perfect cycle.
A basin connects a group of articles and identifies the paths 
to a particular article.

@@

By considering the FLN not only as collection of directly linked pairs of articles, but
as a flow, 
With accumulated references, cycles, and basins, we can explore how the many articles in Wikipedia are organized and related.

@@

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{../graphics/ndegree_loglog.png}
  \caption{
    \textbf{FLN Degree Distribution.}
    We plot the indegree distribution against rank for all articles with an indegree of at least 1 on a $\log_{10}-\log_{10}$. We then fit the data to a power law 
    distribution using the Maximum Likelihood Estimator with xmin as the indegree minimizing Kolmogorov-Smirnov distance. We find xmin to be 5 links with a corresponding power law rank exponent $\alpha = 2.4$ and a size exponent $\gamma = 1.4$.
}
  \label{fig:degree distribution}
\end{figure}

@@

The FLN's in-degree exhibits a decaying power law distribution where a few articles 
receive most direct first references, while most articles receive few or none.
The average in-degree for all 11 million articles is 3.6 direct first links with a standard deviation of 89.5.
Less than $1\%$ of articles have more than 100 direct first links and $75\%$ of articles
have fewer than 9. 
We plot the in-degree distribution against each article's rank with a log-log (base 10) and fit the data to a power law 
distribution using the Maximum Likelihood Estimator with xmin as the indegree minimizing Kolmogorov-Smirnov distance.
(see Fig.~\ref{fig:degree distribution}).
We find xmin to be 5 links with a corresponding power law rank exponent $\alpha = 2.4$ and a size exponent $\gamma = 1.4$. 
Finally, we compare the fit against alternative distributions using a Kolmogorov-Smirnov Test. We find a significant log likelihood ratio favoring a  truncated power law ($R < 0, p=4.5\times10^{-13}$) given the maximum indegree is limited by the number of articles in the FLN. We find an inconclusive log likelihood ratio for a lognormal distribution and significant log likelihood ratios favoring a power law fit against an exponential ($R  > 0, p=0$) and against a stretched exponential ($R > 0, p = 3.0\times10^{-50}$).

@@

Of the 11 million articles, 5.5 million had an invalid link or linked back to the same article, yielding a path length of zero. 
\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{../graphics/traversals_per_article.png} 
  \caption{
    \textbf{Distribution of Traversal Visits.}
    We plot the number of traversal visits for each article by rank on a $\log_{10}-\log_{10}$. We then fit the data to a power law 
    distribution using the Maximum Likelihood Estimator with xmin as the number of traversal visits minimizing Kolmogorov-Smirnov distance. We find xmin to be 866 with a corresponding power law rank exponent $\alpha = 1.7$ and a size exponent $\gamma = 1.6$.
The horizontal flattening around the highest
ranking articles is a result of the cyclic structure (see discussion of Cycles ~\ref{cycles}).
}
  \label{fig:Distribution of Visits}
\end{figure}

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{../graphics/articles_ranked.png}
  \caption{
    \textbf{Highest ranking articles by number of traversal visits.}
We compute the number of traversal visits for each article in the FLN (see 
Sec.~\ref{Traversal Algorithm}). 
In doing so, we can rank each article by the accumulation of first links.
The highest ranking articles by traversal visits reveal where the greatest accumulation occurs.}
  \label{fig:highest visits}
\end{figure}

This roughly corresponds to the official number of articles on Wikipedia: 
$~4.7$ million as of November 2014---approximately half of the 11 million 
articles in the XML dump are redirects or disambiguations, not full articles.
The most common path length is 29, with $75\%$ of path lengths ranging between 7--30 articles.
As a distribution, more than $75\%$ of articles have a path length below 
$50$ first links 
while a few temporally organized paths exceed 50 links 
(see Fig.~\ref{fig:Path Length Distribution}).

@@

\begin{figure*}[tph!]
  \includegraphics[width=\textwidth]{../graphics/2_and_3_cycles.pdf}
  \caption{
    \textbf{Highest ranking 2-cycles and 3-cycles.}
We identify pairs of articles whose first links point to one another, forming
a 2-cycle. We then rank each pair of articles by the total number of 
traversal visits to gauge the most referenced groups of two articles linked
to each other. We find 2-cycles often capture synonyms or articles representing nearly the 
same concepts as opposed to distinct concepts. Similarly, we identify and 
rank 3-cycles to find they appear to capture three closely related ideas or synonyms.}
  \label{fig:cycles}
\end{figure*}
In Fig.~\ref{fig:Distribution of Visits}, we fit traversal visits against a power law distribution using the Maximum Likelihood Estimator with xmin as the number of traversal visits minimizing Kolmogorov-Smirnov distance. We find xmin to be 866 with a corresponding power law rank exponent $\alpha = 1.7$ and a size exponent $\gamma = 1.6$.
We also compared the fit against alternative distributions and found signficiant likelihood ratios favoring a power law fit to an exponential ($R>0, p=2.5\times10^{-60}$) and stretched exponential ($R > 0, p=.0001$).
Similarly to indegree, we found an inconclusive comparison against a lognormal distribution and a signficiant loglikelihood ratio favoring a truncated power law given the max number of traversal visits is restricted by the number of articles in the FLN. 
On the aggregate, the distribution of traversal visits suggests
a handful of the highest ranking articles contain a disproportionate number of traversal visits, while most have none. The skew in the distribution is not terribly surprising when considering the heuristic of how the links flow: from specific to general.

@@

\subsection{Basins}

The highest ranking basins (Sec.~\ref{Traversal Algorithm}) by the number of traversal visits are groups of articles around ``Philosophy.'' 
The highest ranking paths include branches of philosophy flowing through 
``Awareness,'' ``Existence,'' and ``Consciousness'' to ``Philosophy,'' 
which form a cycle of seven articles. As of April 10, 2016 the basin flowing from 
``Philosophy'' has changed to contain instead ``Ancient Greece,'' ``Greek,'' and 
``Indo-European Languages'' (see network resilience Sec.~\ref{Traversal Funnels}).
Other paths
include concepts around ``Mathematics,'' ``Scientific,'' ``Experiments,'' 
``Biology,'' and ``Fact.''
These paths link many specific articles to ``Philosophy,'' each funneled through a particular domain.

Moving beyond basins around ``Philosophy,'' we find other basins around 
foundational concepts such as ``Community,'' ``Landmass,'' ``Federal Government,'' 
``Presentation,'' and ``Belief System.'' 
The basins around each of these foundational notions are 
various paths containing related articles. For example around 
``Community'' we find basins
flowing from ``United States'' to ``Federal Republic'' to ``Political Union'' to ``State'' culminating at ``Community''; we also find basins flowing from 
``Public Policy'' to ``Executive (government)'' to ``Government'' to ``State'' and then 
to ``Community''; we also find paths flowing through a similar chain beginning
with ``Democracy,'' another beginning with ``Constitution,'' another at 
``Dictatorship,'' and so on. The articles build from specific means of organizing
a community (or society) and then build up to ``Community.'' 
Other basins around landmass for example begin at specific geographical regions
such as ``Eastern Europe'' building up to ``Continent'' and finally ``Landmass''.

@@

Among our observations is the appearance of multiple scale-free distributions within the network. 
Few articles have most traversal visits, few paths have an exceptionally long path length, and even fewer
articles are responsible for funneling most paths. When measured against the traversal funnels, 
``Philosophy'' emerges as an exceptional article by orders of magnitude. 
Nevertheless, many other foundational concepts emerged naturally within FLN. 
Basins around ``Community'', ``State'', and ``Science'' reveal a foundational structure within the network. 
More curious is the emergence of recently prominent political and economics topics such as ``Fossil Fuel'' and ``Health Care'' 
within the highest ranking funnels. 
Wikipedia seems to reflect not only timeless foundations, but also the topical (at least within English speaking society).

Future work could examine other language versions of Wikipedia for potentially telling cultural or regional differences as well as expand the network to more than the first link.
These findings also form the basis for the creation of a taxonomy where 
every idea, event, or object sits within a hierarchy of connected notions.
The taxonomy would extend a traditional word thesaurus beyond mere synonyms to a related hierarchy of concepts.
Applications could range from an enhanced network of ideas to psychological insights into how humans form associations.
Specifically, an ever-evolving reference of related hierarchical concepts could be 
used to improve search engine algorithms or natural language processing.

@@

>>>>

\documentclass[pre,twocolumn,twoside,superscriptaddress,floatfix]{revtex4-1}

@@

One possible path through the FLN is a {\it cycle} or a group of articles 
linking to one another inside a loop. In our sample network 
(Fig.~\ref{fig:Traversal Visits}) 
a 3-cycle exists among nodes A, B, and C. 
We can readily identify
the types of cycle structures within the FLN
and rank each by 
the number of references directed towards a cycle. 
We can also identify and rank {\it groups of 
path-connected articles}, not necessarily forming a perfect cycle.

@@

By considering the FLN not only as collection of directly linked pairs of articles, but
as a flow, 
With accumulated references, cycles, and path-connected groups, we can explore how the many articles in Wikipedia are organized and related.

@@

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{../graphics/ndegree_loglog.png}
  \caption{
    \textbf{FLN Degree Distribution.}
    We plot the in-degree distribution against rank for all articles with an in-degree of at least 1 on a $\log_{10}-\log_{10}$. We then fit the data to a power law 
    distribution using the Maximum Likelihood Estimator with xmin as the in-degree minimizing Kolmogorov-Smirnov distance. We find xmin to be 5 links with a corresponding power law rank exponent $\alpha = 2.4$ and a size exponent $\gamma = 1.4$.
}
  \label{fig:degree distribution}
\end{figure}

@@

The FLN's in-degree exhibits a decaying power law distribution where a few articles 
receive most direct first references, while most articles receive few or none.
The average in-degree for all 11 million articles is 3.6 direct first links with a standard deviation of 89.5.
Less than $1\%$ of articles have more than 100 direct first links and $75\%$ of articles
have fewer than 9. 
We plot the in-degree distribution against each article's rank with a log-log (base 10) and fit the data to a power law 
distribution using the Maximum Likelihood Estimator with xmin as the in-degree minimizing Kolmogorov-Smirnov distance
(see Fig.~\ref{fig:degree distribution}) 
\cite{clauset2009power, alstott2014powerlaw}
.
We find xmin to be 5 links with a corresponding power law rank exponent $\alpha = 2.4$ and a size exponent $\gamma = 1.4$. 
We also compare the fit against alternative distributions using the log likelikhood ratio of a Kolmogorov-Smirnov Test 
(see Sec.~\ref{power_law_comp}).

@@

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{../graphics/traversals_per_article.png} 
  \caption{
    \textbf{Distribution of Traversal Visits.}
    We plot the number of traversal visits for each article by rank on a $\log_{10}-\log_{10}$. We then fit the data to a power law 
    distribution using the Maximum Likelihood Estimator with xmin as the number of traversal visits minimizing Kolmogorov-Smirnov distance. We find xmin to be 866 with a corresponding power law rank exponent $\alpha = 1.7$ and a size exponent $\gamma = 1.6$.
The horizontal flattening around the highest
ranking articles is a result of the cyclic structure (see discussion of Cycles ~\ref{cycles}).
}
  \label{fig:Distribution of Visits}
\end{figure}

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{../graphics/articles_ranked.png}
  \caption{
    \textbf{Highest ranking articles by number of traversal visits.}
We compute the number of traversal visits for each article in the FLN (see 
Sec.~\ref{Traversal Algorithm}). 
In doing so, we can rank each article by the accumulation of first links.
The highest ranking articles by traversal visits reveal where the greatest accumulation occurs.}
  \label{fig:highest visits}
\end{figure}
Of the 11 million articles, 5.5 million had an invalid link or linked back to the same article, yielding a path length of zero. 
This roughly corresponds to the official number of articles on Wikipedia: 
$~4.7$ million as of November 2014---approximately half of the 11 million 
articles in the XML dump are redirects or disambiguations, not full articles.
The most common path length is 29, with $75\%$ of path lengths ranging between 7--30 articles.
As a distribution, more than $75\%$ of articles have a path length below 
$50$ first links 
while a few temporally organized paths exceed 50 links 
(see Fig.~\ref{fig:Path Length Distribution}).

@@

\begin{figure*}[tph!]
  \includegraphics[width=\textwidth]{../graphics/2_and_3_cycles.pdf}
  \caption{
    \textbf{Highest ranking 2-cycles and 3-cycles.}
We identify pairs of articles whose first links point to one another, forming
a 2-cycle. We then rank each pair of articles by the total number of 
traversal visits to gauge the most referenced groups of two articles linked
to each other. We find 2-cycles often capture synonyms or articles representing nearly the 
same concepts as opposed to distinct concepts. Similarly, we identify and 
rank 3-cycles to find they appear to capture three closely related ideas or synonyms.}
  \label{fig:cycles}
\end{figure*}
In Fig.~\ref{fig:Distribution of Visits}, we fit traversal visits against a power law distribution using the Maximum Likelihood Estimator with xmin as the number of traversal visits minimizing Kolmogorov-Smirnov distance. We find xmin to be 866 with a corresponding power law rank exponent $\alpha = 1.7$ and a size exponent $\gamma = 1.6$.
We also compared the fit against alternative distributions and found signficiant likelihood ratios favoring a power law fit to an exponential ($R>0, p=2.5\times10^{-60}$) and stretched exponential ($R > 0, p=.0001$).
Similarly to in-degree, we found an inconclusive comparison against a lognormal distribution and a signficiant loglikelihood ratio favoring a truncated power law given the max number of traversal visits is restricted by the number of articles in the FLN. 
On the aggregate, the distribution of traversal visits suggests
a handful of the highest ranking articles contain a disproportionate number of traversal visits, while most have none. The skew in the distribution is not terribly surprising when considering the heuristic of how the links flow: from specific to general.

@@

\subsection{Path-Connected Articles}

The highest ranking groups of path-connected articles (Sec.~\ref{Traversal Algorithm}) by the number of traversal visits are articles around ``Philosophy.'' 
The highest ranking paths include branches of philosophy flowing through 
``Awareness,'' ``Existence,'' and ``Consciousness'' to ``Philosophy,'' 
which form a cycle of seven articles. As of April 10, 2016 the path-connected group around
``Philosophy'' has changed to contain instead ``Ancient Greece,'' ``Greek,'' and 
``Indo-European Languages'' (see network resilience Sec.~\ref{Traversal Funnels}).
Other paths
include concepts around ``Mathematics,'' ``Scientific,'' ``Experiments,'' 
``Biology,'' and ``Fact.''
These paths link many specific articles to ``Philosophy,'' each funneled through a particular domain.

Moving beyond ``Philosophy,'' we find other groups around 
foundational concepts such as ``Community,'' ``Landmass,'' ``Federal Government,'' 
``Presentation,'' and ``Belief System.'' 
The groups around each of these foundational notions are 
contain closely related articles. For example the group connecting
``Community''
flows from ``United States'' to ``Federal Republic'' to ``Political Union'' to ``State'' culminating at ``Community''; we also find groups flowing from 
``Public Policy'' to ``Executive (government)'' to ``Government'' to ``State'' and then 
to ``Community''; we also find paths flowing through a similar chain beginning
with ``Democracy,'' another beginning with ``Constitution,'' another at 
``Dictatorship,'' and so on. The articles build from specific means of organizing
a community (or society) and then build up to ``Community.'' 
Other path-connected groups around landmass for example begin at specific geographical regions
such as ``Eastern Europe'' building up to ``Continent'' and finally ``Landmass''.

@@

Among our observations is the appearance of multiple scale-free distributions within the network. 
Few articles have most traversal visits, few paths have an exceptionally long path length, and even fewer
articles are responsible for funneling most paths. When measured against the traversal funnels, 
``Philosophy'' emerges as an exceptional article by orders of magnitude. 
Nevertheless, many other foundational concepts emerged naturally within FLN. 
Path connected-groups around ``Community'', ``State'', and ``Science'' reveal a foundational structure within the network. 
More curious is the emergence of recently prominent political and economics topics such as ``Fossil Fuel'' and ``Health Care'' 
within the highest ranking funnels. 
Wikipedia seems to reflect not only timeless foundations, but also the topical (at least within English speaking society).

Future work could examine other language versions of Wikipedia for potentially telling cultural or regional differences as well as expand the network to more than the first link.
In addition, the work provides a general algorithm for assessing the structure and measuring influence in a directed network (or any braided flow structure).
These findings also form the basis for the creation of a taxonomy where 
every idea, event, or object sits within a hierarchy of connected notions.
The taxonomy would extend a traditional word thesaurus beyond mere synonyms to a related hierarchy of concepts.
Applications could range from an enhanced network of ideas to psychological insights into how humans form associations.
Specifically, an ever-evolving reference of related hierarchical concepts could be 
used to improve search engine algorithms or natural language processing.

@@

\bibitem{clauset2009power}
A.~Clauset, C.~R. Shalizi, and M.~E. Newman.
\newblock Power-law distributions in empirical data.
\newblock {\em SIAM review}, 51(4):661--703, 2009.

\bibitem{alstott2014powerlaw}
J.~Alstott, E.~Bullmore, and D.~Plenz.
\newblock powerlaw: a python package for analysis of heavy-tailed
  distributions.
\newblock {\em PloS one}, 9(1):e85777, 2014.

### 2016-04-27 writeup/wikipedia-network.tex
draft complete

\begin{abstract}
  \protect
Apples, porcupines, and the most obscure Bob Dylan song---is every topic a few clicks from Philosophy? 
Within Wikipedia, the surprising answer is yes: nearly all 
paths lead to Philosophy.
Wikipedia is the largest, most meticulously indexed collection of human knowledge ever amassed. 
More than information about a topic, Wikipedia is a web of naturally emerging relationships.  
By following the first link in each article, we algorithmically construct a directed network of 
all 4.7 million articles: Wikipedia's First Link Network.
Here, we study the English edition of Wikipedia's First Link Network for insight into how the many 
articles on inventions, places, people, objects, and events are related and organized.  
By traversing every path, we measure the accumulation of first links, path lengths, basins, cycles, 
and the influence each article exerts in shaping the network.
We find scale-free distributions describe path length, 
accumulation, and influence. Far from dispersed, first links disproportionately accumulate 
at a few articles---flowing from specific to general and culminating around fundamental notions such as
Community, State, and Science. 
Philosophy directs more paths than any other article by two orders of magnitude. 
We also observe a gravitation towards topical articles such as 
Health Care and Fossil Fuel. 
These findings enrich our view of the connections and structure of
Wikipedia's ever growing store of knowledge.

@@

%TODO:
% Formatting
    % incorporate into template
% Abstract 
    % Our findings... braided network (not sure I understand what this means? braided networks don't come up in the paper)
        % is the idea to say "we developed an algorithm that's generalizable to a broader class of networks?"
% Method
    % what to cite for drainage basin in geomorphology
    % clarify basin discussion of method
    % cite power law papers (clauset and package)
% Results
    % run MLE; what do i compare against?
\section{Introduction}

@@

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{graphics/ndegree_loglog.png}
  \caption{
    \textbf{FLN Degree Distribution.}
    We plot the indegree distribution against rank for all articles with an indegree of at least 1 on a $\log_{10}-\log_{10}$. We then fit the data to a power law 
    distribution using the Maximum Likelihood Estimator with xmin as the indegree minimizing Kolmogorov-Smirnov distance. We find xmin to be 5 links with a corresponding power law rank exponent $\alpha = 2.4$ and a size exponent $\gamma = 1.4$.
}
  \label{fig:degree distribution}
\end{figure}

@@

Of the 11 million articles, 5.5 million had an invalid link or linked back to the same article, yielding a path length of zero. 
\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{graphics/traversals_per_article.png} 
  \caption{
    \textbf{Distribution of Traversal Visits.}
    We plot the number of traversal visits for each article by rank on a $\log_{10}-\log_{10}$. We then fit the data to a power law 
    distribution using the Maximum Likelihood Estimator with xmin as the number of traversal visits minimizing Kolmogorov-Smirnov distance. We find xmin to be 866 with a corresponding power law rank exponent $\alpha = 1.7$ and a size exponent $\gamma = 1.6$.
The horizontal flattening around the highest
ranking articles is a result of the cyclic structure (see discussion of Cycles ~\ref{cycles}).
}
  \label{fig:Distribution of Visits}
\end{figure}

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{graphics/articles_ranked.png}
  \caption{
    \textbf{Highest ranking articles by number of traversal visits.}
We compute the number of traversal visits for each article in the FLN (see 
Sec.~\ref{Traversal Algorithm}). 
In doing so, we can rank each article by the accumulation of first links.
The highest ranking articles by traversal visits reveal where the greatest accumulation occurs.}
  \label{fig:highest visits}
\end{figure}

This roughly corresponds to the official number of articles on Wikipedia: 
$~4.7$ million as of November 2014---approximately half of the 11 million 
articles in the XML dump are redirects or disambiguations, not full articles.
The most common path length is 29, with $75\%$ of path lengths ranging between 7--30 articles.
As a distribution, more than $75\%$ of articles have a path length below 
$50$ first links 
while a few temporally organized paths exceed 50 links 
(see Fig.~\ref{fig:Path Length Distribution}).

@@

\begin{figure*}[tph!]
  \includegraphics[width=\textwidth]{graphics/2_and_3_cycles.pdf}
  \caption{
    \textbf{Highest ranking 2-cycles and 3-cycles.}
We identify pairs of articles whose first links point to one another, forming
a 2-cycle. We then rank each pair of articles by the total number of 
traversal visits to gauge the most referenced groups of two articles linked
to each other. We find 2-cycles often capture synonyms or articles representing nearly the 
same concepts as opposed to distinct concepts. Similarly, we identify and 
rank 3-cycles to find they appear to capture three closely related ideas or synonyms.}
  \label{fig:cycles}
\end{figure*}
In Fig.~\ref{fig:Distribution of Visits}, we fit traversal visits against a power law distribution using the Maximum Likelihood Estimator with xmin as the number of traversal visits minimizing Kolmogorov-Smirnov distance. We find xmin to be 866 with a corresponding power law rank exponent $\alpha = 1.7$ and a size exponent $\gamma = 1.6$.
We also compared the fit against alternative distributions and found signficiant likelihood ratios favoring a power law fit to an exponential ($R>0, p=2.5\times10^{-60}$) and stretched exponential ($R > 0, p=.0001$).
Similarly to indegree, we found an inconclusive comparison against a lognormal distribution and a signficiant loglikelihood ratio favoring a truncated power law given the max number of traversal visits is restricted by the number of articles in the FLN. 
On the aggregate, the distribution of traversal visits suggests
a handful of the highest ranking articles contain a disproportionate number of traversal visits, while most have none. The skew in the distribution is not terribly surprising when considering the heuristic of how the links flow: from specific to general.

@@

>>>>

\begin{abstract}
  \protect
Apples, porcupines, and the most obscure Bob Dylan song---is every topic a few clicks from Philosophy? 
Within Wikipedia, the surprising answer is yes: nearly all 
paths lead to Philosophy.
Wikipedia is the largest, most meticulously indexed collection of human knowledge ever amassed. 
More than information about a topic, Wikipedia is a web of naturally emerging relationships.  
By following the first link in each article, we algorithmically construct a directed network of 
all 4.7 million articles: Wikipedia's First Link Network.
Here, we study the English edition of Wikipedia's First Link Network for insight into how the many 
articles on inventions, places, people, objects, and events are related and organized.  
By traversing every path, we measure the accumulation of first links, path lengths, cycles, groups of path-connected articles 
and the influence each article exerts in shaping the network.
We find scale-free distributions describe path length, 
accumulation, and influence. Far from dispersed, first links disproportionately accumulate 
at a few articles---flowing from specific to general and culminating around fundamental notions such as
Community, State, and Science. 
Philosophy directs more paths than any other article by two orders of magnitude. 
We also observe a gravitation towards topical articles such as 
Health Care and Fossil Fuel. 
These findings enrich our view of the connections and structure of
Wikipedia's ever growing store of knowledge.

@@

\section{Introduction}

@@

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{graphics/ndegree_loglog.png}
  \caption{
    \textbf{FLN Degree Distribution.}
    We plot the in-degree distribution against rank for all articles with an in-degree of at least 1 on a $\log_{10}-\log_{10}$. We then fit the data to a power law 
    distribution using the Maximum Likelihood Estimator with xmin as the in-degree minimizing Kolmogorov-Smirnov distance. We find xmin to be 5 links with a corresponding power law rank exponent $\alpha = 2.4$ and a size exponent $\gamma = 1.4$.
}
  \label{fig:degree distribution}
\end{figure}

@@

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{graphics/traversals_per_article.png} 
  \caption{
    \textbf{Distribution of Traversal Visits.}
    We plot the number of traversal visits for each article by rank on a $\log_{10}-\log_{10}$. We then fit the data to a power law 
    distribution using the Maximum Likelihood Estimator with xmin as the number of traversal visits minimizing Kolmogorov-Smirnov distance. We find xmin to be 866 with a corresponding power law rank exponent $\alpha = 1.7$ and a size exponent $\gamma = 1.6$.
The horizontal flattening around the highest
ranking articles is a result of the cyclic structure (see discussion of Cycles ~\ref{cycles}).
}
  \label{fig:Distribution of Visits}
\end{figure}

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{graphics/articles_ranked.png}
  \caption{
    \textbf{Highest ranking articles by number of traversal visits.}
We compute the number of traversal visits for each article in the FLN (see 
Sec.~\ref{Traversal Algorithm}). 
In doing so, we can rank each article by the accumulation of first links.
The highest ranking articles by traversal visits reveal where the greatest accumulation occurs.}
  \label{fig:highest visits}
\end{figure}
Of the 11 million articles, 5.5 million had an invalid link or linked back to the same article, yielding a path length of zero. 
This roughly corresponds to the official number of articles on Wikipedia: 
$~4.7$ million as of November 2014---approximately half of the 11 million 
articles in the XML dump are redirects or disambiguations, not full articles.
The most common path length is 29, with $75\%$ of path lengths ranging between 7--30 articles.
As a distribution, more than $75\%$ of articles have a path length below 
$50$ first links 
while a few temporally organized paths exceed 50 links 
(see Fig.~\ref{fig:Path Length Distribution}).

@@

\begin{figure*}[tph!]
  \includegraphics[width=\textwidth]{graphics/2_and_3_cycles.pdf}
  \caption{
    \textbf{Highest ranking 2-cycles and 3-cycles.}
We identify pairs of articles whose first links point to one another, forming
a 2-cycle. We then rank each pair of articles by the total number of 
traversal visits to gauge the most referenced groups of two articles linked
to each other. We find 2-cycles often capture synonyms or articles representing nearly the 
same concepts as opposed to distinct concepts. Similarly, we identify and 
rank 3-cycles to find they appear to capture three closely related ideas or synonyms.}
  \label{fig:cycles}
\end{figure*}
In Fig.~\ref{fig:Distribution of Visits}, we fit traversal visits against a power law distribution using the Maximum Likelihood Estimator with xmin as the number of traversal visits minimizing Kolmogorov-Smirnov distance. We find xmin to be 866 with a corresponding power law rank exponent $\alpha = 1.7$ and a size exponent $\gamma = 1.6$.
We also compared the fit against alternative distributions and found signficiant likelihood ratios favoring a power law fit to an exponential ($R>0, p=2.5\times10^{-60}$) and stretched exponential ($R > 0, p=.0001$).
Similarly to in-degree, we found an inconclusive comparison against a lognormal distribution and a signficiant loglikelihood ratio favoring a truncated power law given the max number of traversal visits is restricted by the number of articles in the FLN. 
On the aggregate, the distribution of traversal visits suggests
a handful of the highest ranking articles contain a disproportionate number of traversal visits, while most have none. The skew in the distribution is not terribly surprising when considering the heuristic of how the links flow: from specific to general.

@@

\subsection{Power Law Alternative Distributions}
\label{power_law_comp}

Using the powerlaw Python package developed by Alstott, we apply MLE to fit a power law exponent and compare the fit to alternative distributions
\cite{clauset2009power, alstott2014powerlaw}.
For in-degree, we find a significant log likelihood ratio favoring a  truncated power law ($R < 0, p=4.5\times10^{-13}$) given the maximum in-degree is limited by the number of articles in the FLN. We find an inconclusive log likelihood ratio for a lognormal distribution and significant log likelihood ratios favoring a power law fit against an exponential ($R  > 0, p=0$) and against a stretched exponential ($R > 0, p = 3.0\times10^{-50}$).
